05_DESeq_manipulation

### 2019-05-18 analysis/05_DESeq2_manipulate.Rmd
now with box plots

pheatmap(sigDEGs, kmeans_k = 5,
         show_rownames = F, show_colnames = F,
         color = viridis(30),
         breaks=myBreaks,
         annotation_col=anndf,
         main = eachgroup)
}
```

>>>>

pheatmap(sigDEGs, kmeans_k = 5,
         show_rownames = F, show_colnames = F,
         color = viridis(30),
         breaks=myBreaks,
         annotation_col=anndf,
         main = eachgroup)
